---
title: "LTER: SiSyn"
date: "7/26/2021"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

1. Develop a function to evaluate C-Q relationships that includes several different modeling approaches. 

**Models:**

  - Log-Linear (power law): $C=\alpha Q^{\beta}$ or the linearized version of  $log(C) = \beta log(\alpha) + log(Q)$.
  
  - Segmented: (with one break point)
  
<center>$log(C) = \beta_{1} log(\alpha_1) + log(Q)$ for Q < Break point </center>
<br>
<center>$log(C) = \beta_{2} log(\alpha_2) + log(Q)$ for Q > Break point </center>
<br>
Breakpoints are determined through an iterative process and identified when the linear relationship changes. The model is estimated simultaneously yielding point estimates and relevant approximate standard errors of all the model parameters, including the break-points.

  - *"Moatar"*: <mark><u>Similar to segmented regression with a pre-defined breakpoint</u></mark>. Based on analyses presented by [Moatar et al. (2017)](https://agupubs.onlinelibrary.wiley.com/doi/10.1002/2016WR019635){target="_blank"}. Individual slopes were estimated for discharges below and above the median daily discharge ($\beta_{50inf}$ and $\beta_{50sup}$, respectively where *"inf"* = inferior (below) and *"sup"* = superior (above)). The predicted concentrations for both models were averaged. 

## Function

```{r, include=T,eval=F}
# To check and install if needed packages
check.packages <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

pkg=c("segmented","gvlma")
check.packages(pkg)

```

```{r, include=T}
library(segmented)
library(gvlma)
#' Fitting models to Concentration-Discharge data using several different 
#' models/methods and extracting relevat information

#' @param logQ       log transformed paired discharge value
#' @param logC       log transformed paired concentration value
#' @param Q50        median value of daily discharge 
#' @param plot       default = TRUE; identifies if you want to plot results.
#' @param models     default = c("log-linear","segmented","moatar"); identified
#'                   what models to plot
#' @param plot.CI    default = TRUE; If the models are plotted a 95% confidence 
#'                   interval will also be plotted
#' @param CI.level   default = 0.95; confidence interval level
#' @param plot.lwd   default = 1.5; model line thickness
#' @param legend.pos default = "topleft"; legend position if models are plotted
#' @param print.rslt defualt = TRUE; print output table. 
#' @param ...        other plotting variables see ?plot (i.e. pch, lwd, bg, col, ylim, etc.)

CQ_fun=function(logQ,logC,Q50,plot=TRUE,
                models=c("log-linear","segmented","moatar"),
                plot.CI=TRUE,
                CI.level=0.95,
                plot.lwd=1.5,
                legend.pos="topleft",
                print.rslt=TRUE,...){
  
  # Power Law
  loglog.mod=lm(logC~logQ)
  loglog.mod.sum=summary(loglog.mod)
  
  # Check assumptions
  LL.assump=gvlma(loglog.mod)
  asumpt.rslt=as.character(ifelse(LL.assump$GlobalTest$GlobalStat4$pvalue<0.05,"No","Yes"))
  
  # variabled of interest
  loglog.beta=as.numeric(coef(loglog.mod)[2])
  loglog.alpha=as.numeric(coef(loglog.mod)[1])
  
  LL.rslt=data.frame(LL.R2=loglog.mod.sum$r.squared,
                     LL.R2.adj=loglog.mod.sum$adj.r.squared,
                     LL.RMSE=loglog.mod.sum$sigma,
                     LL.beta=loglog.beta,
                     LL.beta.SE=loglog.mod.sum$coefficients[2,2],
                     LL.beta.tval=loglog.mod.sum$coefficients[2,3],
                     LL.beta.pval=loglog.mod.sum$coefficients[2,4],
                     LL.alpha=loglog.alpha,
                     LL.AIC=AIC(loglog.mod),
                     LL.BIC=BIC(loglog.mod),
                     LL.LogLik=as.numeric(logLik(loglog.mod)),
                     LL.assumpt.pass=asumpt.rslt)
  
  # Segmented
  # Picks 1st breakpoint
  loglog.mod.seg=segmented(loglog.mod,seg.Z=~logQ)
  loglog.mod.seg.sum=summary(loglog.mod.seg)
  
  # is there a breakpoint?
  if(nrow(loglog.mod.seg$psi)==0){
    seg.psi.est=NA
    seg.psi.SE=NA
  }else{
    seg.psi.est=loglog.mod.seg$psi[1,c(2)]
    seg.psi.SE=seg.psi=loglog.mod.seg$psi[1,c(3)]
  }
  
  seg.rslt=data.frame(seg.bk.est=exp(seg.psi.est),
                      seg.bk.SE=exp(seg.psi.SE),
                      seg.R2=loglog.mod.seg.sum$r.squared,
                      seg.R2.adj=loglog.mod.seg.sum$adj.r.squared,
                      seg.RMSE=loglog.mod.seg.sum$sigma,
                      seg.AIC=AIC(loglog.mod.seg),
                      seg.BIC=BIC(loglog.mod.seg),
                      seg.LogLik=as.numeric(logLik(loglog.mod.seg)))
  
  # Moatar
  logQ.m=logQ[logQ<log(Q50)]
  logC.m=logC[logQ<log(Q50)]
  loglog.mod.inf=lm(logC.m~logQ.m)
  loglog.mod.inf.sum=summary(loglog.mod.inf)
  CQ50.inf=predict(loglog.mod.inf,data.frame(logQ.m=log(Q50)))

  logQ.m=logQ[logQ>log(Q50)]
  logC.m=logC[logQ>log(Q50)]
  loglog.mod.sup=lm(logC.m~logQ.m)
  loglog.mod.sup.sum=summary(loglog.mod.sup)
  CQ50.sup=predict(loglog.mod.sup,data.frame(logQ.m=log(Q50)))

  moatar.rslt=data.frame(Q50=Q50,
                         moatar.beta.inf=as.numeric(coef(loglog.mod.inf)[2]),
                         moatar.R2.inf=loglog.mod.inf.sum$r.squared,
                         moatar.R2.adj.inf=loglog.mod.inf.sum$adj.r.squared,
                         moatar.RMSE.inf=loglog.mod.inf.sum$sigma,
                         moatar.beta.sup=as.numeric(coef(loglog.mod.sup)[2]),
                         moatar.R2.sup=loglog.mod.sup.sum$r.squared,
                         moatar.R2.adj.sup=loglog.mod.sup.sum$adj.r.squared,
                         moatar.RMSE.sup=loglog.mod.sup.sum$sigma,
                         moatar.C_Q50=exp(mean(c(CQ50.inf,CQ50.sup))))
  
  rslt.all=cbind(LL.rslt,seg.rslt,moatar.rslt)
  
  # Plotting
  if(plot==T){
    plot(dat.CQ$Si~dat.CQ$Q,log="xy",...)
    
    if(sum(match(models,"log-linear"),na.rm=T)==1){
    x.val=seq(min(logQ,na.rm=T),max(logQ,na.rm=T),length.out=70)
    LL.pred=predict(loglog.mod,data.frame(logQ=x.val),interval="confidence",
                    level=CI.level)
    lines(exp(x.val),exp(LL.pred[,1]),col="red",lwd=plot.lwd)
    if(plot.CI==T){
    lines(exp(x.val),exp(LL.pred[,2]),col="red",lty=2)
    lines(exp(x.val),exp(LL.pred[,3]),col="red",lty=2)
    }
    }
    
    if(sum(match(models,"segmented"),na.rm=T)==1){
      x.val=seq(min(logQ,na.rm=T),max(logQ,na.rm=T),length.out=70)
    seg.pred=predict(loglog.mod.seg,data.frame(logQ=x.val),
                     interval="confidence",level=CI.level)
    lines(exp(x.val),exp(seg.pred[,1]),col="blue",lwd=plot.lwd)
    if(plot.CI==T){
    lines(exp(x.val),exp(seg.pred[,2]),col="blue",lty=2)
    lines(exp(x.val),exp(seg.pred[,3]),col="blue",lty=2)
    }
    }
    
    if(sum(match(models,"moatar"),na.rm=T)==1){
      abline(v=Q50)
      x.val=seq(min(logQ,na.rm=T),log(Q50),length.out=50)
      LL.inf=predict(loglog.mod.inf,data.frame(logQ.m=x.val),
                     interval="confidence",level=CI.level)          
      lines(exp(x.val),exp(LL.inf[,1]),col="forestgreen",lwd=plot.lwd)
      if(plot.CI==T){
      lines(exp(x.val),exp(LL.inf[,2]),col="forestgreen",lty=2)
      lines(exp(x.val),exp(LL.inf[,3]),col="forestgreen",lty=2)
      }
      
      x.val=seq(log(Q50),max(logQ,na.rm=T),length.out=50)
      LL.sup=predict(loglog.mod.sup,data.frame(logQ.m=x.val),
                     interval="confidence",level=CI.level)          
      lines(exp(x.val),exp(LL.sup[,1]),col="forestgreen")
      if(plot.CI==T){
      lines(exp(x.val),exp(LL.sup[,2]),col="forestgreen",lty=2)
      lines(exp(x.val),exp(LL.sup[,3]),col="forestgreen",lty=2)
      }
    }
    
    mod.col=c("red","blue","forestgreen")
    mod.col=mod.col[match(models,c("log-linear","segmented","moatar"))]
    legend.pos=if(is.na(legend.pos)==T){"topleft"}else(legend.pos)
    legend(legend.pos,
           legend=models,
           lty=1,
           col=mod.col,
           ncol=1,bty="n",y.intersp=1,x.intersp=0.75,
           xpd=NA,xjust=0.5,yjust=0.5,title="Model",title.adj = 0)
  
  }
  if(print.rslt==TRUE){return(rslt.all)}
}


```


Output includes measure of relative and absolute fit, slopes and intercepts and breakpoints as a `data.frame`.

* `LL.R2` : Log-linear R^2^
* `LL.R2.adj` : Log-linear adjusted R^2^
* `LL.RMSE` : Log-linear Root Mean Square Error
* `LL.beta` : Log-linear slope
* `LL.beta.SE`: Log-linear slope standard error
* `LL.beta.tval` : Log-linear slope t-value (different from zero)
* `LL.beta.pval` : Log-linear slope p-value (different from zero)
* `LL.alpha` : Log-linear intercept
* `LL.AIC`: Log-Linear AIC
* `LL.BIC`: Log-Linear BIC
* `LL.LogLik`: Log-Linear log-likelihood (used to calculate AIC and BIC)
* `LL.assumpt.pass`: uses `gvlma` package to test linear model assumptions, extracts global test decision.
* `seg.bk.est` : Segmented regression break point (if one is detected). Only reports first break point if more than one is detected (back-transformed)
* `seg.bk.SE` : Segmented regression break point standard error (back-transformed)
* `seg.R2` : Segmented R^2^
* `seg.R2.adj` : Segmented adjusted R^2^
* `seg.RMSE` : Segmented Root Mean Square Error
* `seg.AIC`: Segmented AIC
* `seg.BIC`: Segmented BIC
* `seg.LogLik`: Segmented log-likelihood (used to calculate AIC and BIC)
* `Q50` : Median discharge value used in function input
* `moatar.beta.inf` : Slope of C-Q below the median discharge value
* `moatar.R2.inf` : R^2^ of C-Q below the median discharge value
* `moatar.R2.adj.inf` : Adjusted R^2^ of C-Q below the median discharge value
* `moatar.RMSE.inf` :  Root Mean Square Error of C-Q below the median discharge value
* `moatar.beta.sup` : Slope of C-Q above the median discharge value
* `moatar.R2.sup` : R^2^ of C-Q above the median discharge value
* `moatar.R2.adj.sup` : Adjusted R^2^ of C-Q above the median discharge value
* `moatar.RMSE.sup` :  Root Mean Square Error of C-Q above the median discharge value
* `moatar.C_Q50` : Averaged predicted concentration at median discharge


***

## Examples

### UMR: M786.2

```{r,include=T,fig.align='center',fig.cap="C-Q relationship of M786.2 (UMR; all data) and all models"}
# read discharge data
dat.Q=read.csv("./Data/M786.2C_Q_WRTDS.csv")
dat.Q$Date=as.Date(dat.Q$Date)# identify date

# read concentration data
dat.C=read.csv("./Data/M786.2C_Si_WRTDS.csv")
dat.C$Date=as.Date(dat.C$Date)# identify date

# merge the C and Q data
dat.CQ=merge(dat.Q,dat.C,"Date")

Q50=median(dat.Q$Q,na.rm=T)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,pch=19,ylim=c(1,10),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)")
```

Here is an example of plotting each individual model without individual data points, and output suppressed. 

```{r, include=T,fig.width=4,fig.height=5,fig.align='center',fig.cap="C-Q relationship of M786.2 (UMR; all data) and all models with individual data points removed from the plot"}
par(mar=c(2,4,1,1),oma=c(3,1,1,1),mgp=c(2,1,0))
layout(matrix(1:3,3,1))
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,10),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="log-linear",
       print.rslt=F)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,10),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="segmented",
       print.rslt=F)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,10),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="moatar",
       print.rslt=F,
       xpd=NA)
```


### LUQ: MPR

```{r,include=T,fig.align='center',fig.cap="C-Q relationship of MPR (LUQ; all data) and all models"}
# read discharge data
dat.Q=read.csv("./Data/MPR_Q_WRTDS.csv")
dat.Q$Date=as.Date(dat.Q$Date)# identify date

# read concentration data
dat.C=read.csv("./Data/MPR_Si_WRTDS.csv")
dat.C$Date=as.Date(dat.C$Date)# identify date

# merge the C and Q data
dat.CQ=merge(dat.Q,dat.C,"Date")

Q50=median(dat.Q$Q,na.rm=T)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,pch=19,ylim=c(1,50),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       main="LUQ MPR")
```

```{r, include=T,fig.width=4,fig.height=5,fig.align='center',fig.cap="C-Q relationship of MPR (LUQ; all data) and all models with individual data points removed from the plot"}
par(mar=c(2,4,1,1),oma=c(3,1,1,1),mgp=c(2,1,0))
layout(matrix(1:3,3,1))
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,50),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="log-linear",
       print.rslt=F)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,50),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="segmented",
       print.rslt=F)
CQ_fun(log(dat.CQ$Q),log(dat.CQ$Si),Q50,plot.CI=T,ylim=c(1,50),
       legend.pos = "bottomright",
       ylab="Si Concentration (mg/L)",
       xlab="Discharge (cfs)",
       type="n",
       models="moatar",
       print.rslt=F,
       xpd=NA)
```
***
