---
title: "Analytes by site"
output: html_document
---

# Setup

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(knitr)
library(psych)
library(GGally)
library(ggfortify)
library(cluster)
library(lubridate)

theme_set(theme_bw()+
            theme(axis.text=element_text(size=8),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16)))

select <- dplyr::select
```


> Make matrix of site vs counts of observations of each analyte - including ALL SITES for now, not just our long term ones

```{r echo=TRUE}

sisyn <- read_csv("20201111_masterdata_RAW.csv")

thematrix <- sisyn %>%
  select(LTER, site, variable, value) %>%
  count(LTER, site, variable, sort=TRUE) %>% 
  pivot_wider(names_from = variable, values_from = n)%>% 
  filter(!is.na(site)) #%>% 
#  column_to_rownames(var="site")

thematrix[is.na(thematrix)] <- 0 #turns NAs into zeros

kable(head(thematrix))

```

>INSERT SAME^ BUT ONLY LONG TERM SITES at some point to see if patterns are different at all

# Variable counts - all sites - no filtering by length of record

> # Total # observations by analyte as we have seen before

```{r}
sisyn %>% count(variable, sort = TRUE) %>% kable()
```

> # Observations of analyte by LTER (a lot to scroll through but you kinda see which sites have lots of what)

```{r}
sisyn %>% count(LTER, variable, sort = TRUE) %>% kable()
#sisyn %>% count(LTER, site, variable, sort = TRUE) %>% kable()

```

## Correlations among observation counts of some key analytes

> There are 33 analytes so it's tricky to look at those all at once, but here's a subset of what should be important. The point here is just that more observations of one thing is correlated with more observations of other stuff within a site, and most sites that have lots of DSi data *usually* also have N and P data

```{r}
thematrix %>% 
  select(DSi, NOx, NH4, PO4) %>% 
  pairs.panels(scale = TRUE)
```

> also the lower left wedge area looks like a good target for things that are measured at the same time + place as DSi (and their ratios)

```{r}
thematrix %>% 
  ggcorr()

#thematrix %>% 
 # select(DSi, NOx, NH4, PO4) %>% 
  #ggpairs()
```

> correlations between DSi and other stuff

```{r}
x <- thematrix %>% 
  select(DSi, NOx, SO4, DOC, NH4, PO4, TSS, TN, TP,
         TDN, SRP, Suspended.Chl, DIN, VSS) %>% 
  corr.test()

x <- x[["r"]]
x[1,]

x

```


## PCA: clustering of analytes by site

```{r}
pca1 <- prcomp(thematrix[3:35])
summary(pca1, size = 4)
#autoplot(pca1)
```

> looks like maybe 2 distinct clusters - those with lots DSi, NOx, NO4, SO4, PO4 etc and then a couple with lots of TN, TP, chl, etc

```{r}
autoplot(prcomp(thematrix[3:35]), data = thematrix, colour = 'LTER', loadings=TRUE, loadings.label=TRUE, size = 4)

#it really didn't like the names for discharge and thought it was a function

thematrix <- thematrix %>% 
  rename(IQ=`Instantaneous.Q.(Discharge)`) %>% 
  rename(DQ = `Daily.Avg.Q.(Discharge)`)
```

> or maybe 3 clusters - those with few data points (probably not super long term sites), then those with lots of data points but going either in the direction of TN/TP or NOx/PO4?

```{r}
autoplot(fanny(thematrix[3:35], 3), frame=TRUE, frame.type='norm', data = thematrix, size = 4)

#autoplot(fanny(pca1, frame = TRUE,label=TRUE))

```


# Variable counts - only long term sites

> filtering to get just the LTERs we will mostly focus on with long-term data (I think)

```{r, echo=TRUE}

# I think these are the right long term LTERS????
longtermLTERs <- c("ARC", "AND", "KRR(Julian)", "LMP(Wymore)", "LUQ", "MCM", "NWT", "Sagehen(Sullivan)", "UMR(Jankowski)")

thematrix2 <-  thematrix %>%
  filter(LTER %in% longtermLTERs)

```

> looks same as with all sites, at least that lower left wedge

```{r}
thematrix2 %>% 
  ggcorr()
```


```{r}

autoplot(prcomp(thematrix2[3:35]), data = thematrix2, colour = 'LTER', loadings=TRUE, loadings.label=TRUE, size = 4)


autoplot(fanny(thematrix[3:35], 3), frame=TRUE, frame.type='norm', data = thematrix, size = 4)
```

> another way to look at which of the long-term sites have what

```{r}

sisyn2 <- sisyn %>% 
  filter(LTER %in% longtermLTERs) %>% 
  count(LTER, site, variable, sort=TRUE)
  
ggplot(sisyn2, aes(variable, n))+
  geom_boxplot()+
  facet_wrap(~LTER)+
  coord_flip()

sisyn2 %>% 
  filter(variable %in% c("PO4", "NOx", "DSi")) %>% 
  ggplot(aes(variable, n))+
  geom_boxplot()+
  facet_wrap(~LTER)+
  coord_flip()

sisyn2 %>% 
  filter(variable %in% c("TP", "TN", "DSi")) %>% 
  ggplot(aes(variable, n))+
  geom_boxplot()+
  facet_wrap(~LTER)+
  coord_flip()


```


# Finding which sites have >15 years of DSi, NOx, PO4, SRP data


> long data approach

```{r}
# making year into its own column

sisyn <- sisyn %>% 
  mutate(sample.date=date(Sampling.Date)) %>%  
  mutate(year=year(sample.date))

si_range <- sisyn %>%
  group_by(LTER, site, variable) %>% 
  summarize(first_year=min(year), last_year=max(year),
            num_observations = n()) %>% 
  mutate(time_range = last_year-first_year) %>% 
  mutate(obs_per_year=num_observations/time_range)

ggplot(si_range, aes(time_range, num_observations))+
  geom_point()

long_term <- si_range %>% 
  filter(time_range>14) %>% 
  filter(variable %in% c("DSi", "NOx", "PO4", "SRP", "TN", "TP"))

ggplot(long_term, aes(time_range, num_observations, color=LTER))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~variable, scales = 'free')

long_term_wide <- long_term %>% 
  pivot_wider(names_from = variable, values_from = c(time_range, num_observations, obs_per_year))


long_term_wide2 <- long_term %>%
  select(-first_year, -last_year) %>% 
  pivot_wider(names_from = variable, values_from = c(time_range, num_observations, obs_per_year))

long_term %>% group_by(variable) %>% 
  summarize(sum(num_observations))

dim(long_term_wide2)

long_term_wide2 %>% 
  filter(is.na(time_range_TN)) %>% 
  dim()
long_term_wide2 %>% 
  filter(is.na(time_range_TP)) %>% 
  dim()

#write.csv(long_term_wide, "long_term_wide.csv")
#write.csv(long_term_wide2, "long_term_wide2.csv")
#write.csv(long_term_wide2, "long_term_wide_TNTP.csv")

```


```{r}
```


```{r}
```


```{r}
```


