---
title: "DSi fluxes, FN concentrations, etc from WRTDS over time"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    collapsed: false
---


# Setup and data wrangling

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(broom)
library(ggridges)
library(ggpubr)
library(knitr)
library(PerformanceAnalytics)
library(car)
library(MASS)
library(lubridate)
library(scales)
library(lme4)
library(nlme)
library(metafor)
library(psych)
library(metaviz)
library(leaflet)

theme_set(theme_bw()+
            theme(axis.text=element_text(size=8),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16)))

knitr::opts_chunk$set(fig.width=12, fig.height=8, 
                      fig.path='Figs/Effect sizes and forest plots/', 
                      echo=TRUE, warning=FALSE, message=FALSE)


select <- dplyr::select

# function to give sample sizes (here, number of sites per LTER)
give.n <- function(x){
  return(c(y = mean(x), label = length(x)))
}


```

> reading files and adding/checking LTER names

```{r}

sisyn <- read_csv("20201111_masterdata_RAW.csv") 

wrtds_annual <- read_csv("WRTDS_AnnualResults_AllSites_052621.csv") %>% 
  rename(site=Site)

wrtds_trends <- read_csv("Si_EGRETCi_Trends_AllSites.csv") %>% 
  rename(site=Site)



sisyn_sites <- sisyn %>%  select(site, LTER) %>% unique()

wrtds_annual <- left_join(wrtds_annual, sisyn_sites)

wrtds_trends <- left_join(wrtds_trends, sisyn_sites) %>% 
  mutate(LTER_site=paste(LTER, site, sep = "------"))

x <- wrtds_annual %>% filter(is.na(LTER))
unique(x$site)

wrtds_annual <- wrtds_annual %>% 
  mutate(LTER=ifelse(is.na(LTER), "HBR", LTER))

wrtds_trends <- wrtds_trends %>% 
  mutate(LTER=ifelse(is.na(LTER), "HBR", LTER))

z <- wrtds_annual %>% count(LTER,site)
z

```

> pivoting the annual discharge/flux/conc/FNconc data and then calculating correlations and regressions across time

```{r}
wrtds_long <- wrtds_annual %>%
  pivot_longer(cols = c(Discharge_cms:FNFlux_106_kg_y),
               names_to = "variable",
               values_to = "value")

#correlations:
wrtds_corr <- wrtds_long %>% 
  group_by(site, LTER, variable) %>% 
  summarize(ri=cor(Year, value, use = "pairwise.complete.obs"), ni=n())


#regressions:
wrtds_slopes <-  wrtds_long %>%
  filter(!is.na(value)) %>% 
  group_by(site, LTER, variable) %>%
  do(model = tidy(lm(value ~ Year, data = .))) %>% # only works if you include the broom::tidy in here
  unnest(model)



```

# Correlations/slopes from annual estimates

```{r}

ggplot(wrtds_corr, aes(LTER, ri)) + 
    stat_summary(fun = mean, geom = "point") + 
    stat_summary(fun.data = mean_cl_normal, geom = "pointrange", fun.args = list(mult = 1))+
  geom_hline(yintercept = 0)+
  xlab("LTER")+
  ylab("correlation of DSi ~ year")+
  stat_summary(fun.data = give.n, geom = "text", size=3, fontface="italic", position = position_nudge(x = 0.4, y=.1))+
  coord_flip()+
  scale_x_discrete(limits = rev)+
  facet_wrap(~variable)


ggplot(wrtds_corr, aes(site, ri)) + 
    stat_summary(fun = mean, geom = "point") + 
    stat_summary(fun.data = mean_cl_normal, geom = "pointrange", fun.args = list(mult = 1))+
  geom_hline(yintercept = 0)+
  xlab("LTER")+
  ylab("correlation of DSi ~ year")+
  stat_summary(fun.data = give.n, geom = "text", size=3, fontface="italic", position = position_nudge(x = 0.4, y=.1))+
  coord_flip()+
  scale_x_discrete(limits = rev)+
  facet_wrap(~variable)

```

> discharge is super correlated to flux but not conc across sites and years? does this make sense?

```{r}
pairs.panels(wrtds_annual)

```

> models using correlation data

```{r}

ES_wrtds <- escalc(measure="ZCOR", ri=ri, ni=ni, data=wrtds_corr)

mod1<-rma(yi=yi,vi=vi,data=filter(ES_wrtds, variable=='Discharge_cms'))
summary(mod1)

mod2<-rma(yi=yi,vi=vi,data=filter(ES_wrtds, variable=='Conc_mgL'))
summary(mod2)

mod3<-rma(yi=yi,vi=vi,data=filter(ES_wrtds, variable=='FNConc_mgL'))
summary(mod3)

mod3.1<-rma(yi=yi,vi=vi,data=filter(ES_wrtds, variable=='FNConc_mgL'),
            mods = ~LTER)
summary(mod3.1)
```


## meta-regression models

```{r}
wrtds_slopes <- left_join(wrtds_slopes, wrtds_corr) %>% 
  mutate(mi=1) %>% 
  filter(term=='Year')

wrtds_slopes <- wrtds_slopes %>% 
  arrange(LTER)

wrtds_slopes_ES_Si <- escalc(measure='ZPCOR',
                          ti=statistic,
                          ni=ni,
                          mi=mi,
                          data=filter(wrtds_slopes, variable=='Conc_mgL'))

wrtds_slopes_ES_discharge <- escalc(measure='ZPCOR',
                          ti=statistic,
                          ni=ni,
                          mi=mi,
                          data=filter(wrtds_slopes, variable=='Discharge_cms'))

wrtds_slopes_ES_flux <- escalc(measure='ZPCOR',
                          ti=statistic,
                          ni=ni,
                          mi=mi,
                          data=filter(wrtds_slopes, variable=='Flux_106_kg_y'))


mod_Si1<-rma.mv(yi,vi,
          data=filter(wrtds_slopes_ES_Si),
          random = ~1|site)
summary(mod_Si1)
forest(mod_Si1)

mod_Si2<-rma.mv(yi,vi,
          data=filter(wrtds_slopes_ES_Si))
summary(mod_Si2)
forest(mod_Si2)

mod_discharge1<-rma.mv(yi,vi,
          data=filter(wrtds_slopes_ES_discharge),
          random = ~1|site)
summary(mod_discharge1)
forest(mod_discharge1)


mod_flux1<-rma.mv(yi,vi,
          data=filter(wrtds_slopes_ES_flux),
          random = ~1|site)
summary(mod_flux1)
forest(mod_flux1)

viz_forest(x = wrtds_slopes_ES_Si[, c("yi", "vi")], 
           study_labels = wrtds_slopes_ES_Si[, "site"],
           xlab = "Slope of Si by year (Z-transformed)",
           variant = "thick",
           group=wrtds_slopes_ES_Si[, "LTER"],
           method = "REML",
           annotate_CI = TRUE,
           summary_label = c("Summary(LTER = AND)",
                  "Summary(LTER = ARC)",
                  "Summary(LTER = KRR(Julian))",
                  "Summary(LTER = HBR)",
                  "Summary(LTER = LMP(Wymore))",
                  "Summary(LTER = LUQ)",
                  "Summary (LTER = MCM)",
                  "Summary (LTER = NWT)",
                   "Summary(LTER = Sagehen(Sullivan))",
                   "Summary(LTER = UMR(Jankowski))"))
```

## forest plots for modeled DSi conc by LTER

```{r}

a <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="AND")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="AND")[, "site"],
           xlab = "ANDREWS: Slope of DSi by year (Z-transf.)",
           variant = "rain")
a     

b <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="ARC")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="ARC")[, "site"],
           xlab = "ARCTIC: Slope of DSi by year (Z-transf.)",
           variant = "rain")
b    
c <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="HBR")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="HBR")[, "site"],
           xlab = "HUBBARD BROOK: Slope of DSi by year (Z-transf.)",
           variant = "rain")
c
d <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="KRR(Julian)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="KRR(Julian)")[, "site"],
           xlab = "KISSIMMEE: Slope of DSi by year (Z-transf.)",
           variant = "rain")
d

e <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="LMP(Wymore)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="LMP(Wymore)")[, "site"],
           xlab = "LAMPREY: Slope of DSi by year (Z-transf.)",
           variant = "rain")
e

f <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="LUQ")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="LUQ")[, "site"],
           xlab = "LUQUILLO: Slope of DSi by year (Z-transf.)",
           variant = "rain")
f

g <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="MCM")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="MCM")[, "site"],
           xlab = "MCMURDO: Slope of DSi by year (Z-transf.)",
           variant = "rain")
g

h <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="NWT")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="NWT")[, "site"],
           xlab = "NIWOT: Slope of DSi by year (Z-transf.)",
           variant = "rain")
h

i <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="Sagehen(Sullivan)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="Sagehen(Sullivan)")[, "site"],
           xlab = "Sagehen: Slope of DSi by year (Z-transf.)",
           variant = "rain")
i

j <- viz_forest(x = filter(wrtds_slopes_ES_Si, LTER=="UMR(Jankowski)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_Si, LTER=="UMR(Jankowski)")[, "site"],
           xlab = "Sagehen: Slope of DSi by year (Z-transf.)",
           variant = "rain")
j

ggarrange(a,b,c,d,e,f,g,h,i,j, ncol=5, nrow=2)


viz_forest(x = wrtds_slopes_ES_Si[, c("yi", "vi")], 
           xlab = "Slope of DSi by year (Z-transformed)",
           group=wrtds_slopes_ES_Si[, "LTER"],
           variant = "rain",
           study_labels = wrtds_slopes_ES_Si[, "site"],
           summary_label = c("Summary(LTER = AND)",
                  "Summary(LTER = ARC)",
                  "Summary(LTER = KRR(Julian))",
                  "Summary(LTER = HBR)",
                  "Summary(LTER = LMP(Wymore))",
                  "Summary(LTER = LUQ)",
                  "Summary (LTER = MCM)",
                  "Summary (LTER = NWT)",
                   "Summary(LTER = Sagehen(Sullivan))",
                   "Summary(LTER = UMR(Jankowski))"))

```

## forest plots for discharge

```{r}

a <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="AND")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="AND")[, "site"],
           xlab = "ANDREWS: Slope of discharge by year (Z-transf.)",
           variant = "rain")
a     

b <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="ARC")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="ARC")[, "site"],
           xlab = "ARCTIC: Slope of discharge by year (Z-transf.)",
           variant = "rain")
b    
c <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="HBR")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="HBR")[, "site"],
           xlab = "HUBBARD BROOK: Slope of discharge by year (Z-transf.)",
           variant = "rain")
c
d <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="KRR(Julian)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="KRR(Julian)")[, "site"],
           xlab = "KISSIMMEE: Slope of discharge by year (Z-transf.)",
           variant = "rain")
d

e <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="LMP(Wymore)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="LMP(Wymore)")[, "site"],
           xlab = "LAMPREY: Slope of discharge by year (Z-transf.)",
           variant = "rain")
e

f <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="LUQ")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="LUQ")[, "site"],
           xlab = "LUQUILLO: Slope of discharge by year (Z-transf.)",
           variant = "rain")
f

g <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="MCM")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="MCM")[, "site"],
           xlab = "MCMURDO: Slope of discharge by year (Z-transf.)",
           variant = "rain")
g

h <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="NWT")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="NWT")[, "site"],
           xlab = "NIWOT: Slope of discharge by year (Z-transf.)",
           variant = "rain")
h

i <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="Sagehen(Sullivan)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="Sagehen(Sullivan)")[, "site"],
           xlab = "Sagehen: Slope of discharge by year (Z-transf.)",
           variant = "rain")
i

j <- viz_forest(x = filter(wrtds_slopes_ES_discharge, LTER=="UMR(Jankowski)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_discharge, LTER=="UMR(Jankowski)")[, "site"],
           xlab = "Sagehen: Slope of discharge by year (Z-transf.)",
           variant = "rain")
j

ggarrange(a,b,c,d,e,f,g,h,i,j, ncol=5, nrow=2)



viz_forest(x = wrtds_slopes_ES_discharge[, c("yi", "vi")], 
           xlab = "Slope of discharge by year (Z-transformed)",
           group=wrtds_slopes_ES_discharge[, "LTER"],
           study_labels = wrtds_slopes_ES_discharge[, "site"],
           variant = "rain",
           summary_label = c("Summary(LTER = AND)",
                  "Summary(LTER = ARC)",
                  "Summary(LTER = KRR(Julian))",
                  "Summary(LTER = HBR)",
                  "Summary(LTER = LMP(Wymore))",
                  "Summary(LTER = LUQ)",
                  "Summary (LTER = MCM)",
                  "Summary (LTER = NWT)",
                   "Summary(LTER = Sagehen(Sullivan))",
                   "Summary(LTER = UMR(Jankowski))"))

```

## forest plots for flux

```{r}

a <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="AND")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="AND")[, "site"],
           xlab = "ANDREWS: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
a     

b <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="ARC")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="ARC")[, "site"],
           xlab = "ARCTIC: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
b    
c <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="HBR")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="HBR")[, "site"],
           xlab = "HUBBARD BROOK: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
c
d <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="KRR(Julian)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="KRR(Julian)")[, "site"],
           xlab = "KISSIMMEE: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
d

e <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="LMP(Wymore)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="LMP(Wymore)")[, "site"],
           xlab = "LAMPREY: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
e

f <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="LUQ")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="LUQ")[, "site"],
           xlab = "LUQUILLO: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
f

g <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="MCM")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="MCM")[, "site"],
           xlab = "MCMURDO: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
g

h <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="NWT")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="NWT")[, "site"],
           xlab = "NIWOT: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
h

i <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="Sagehen(Sullivan)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="Sagehen(Sullivan)")[, "site"],
           xlab = "Sagehen: slope of DSi flux by year (Z-transf.)",
           variant = "rain")
i

j <- viz_forest(x = filter(wrtds_slopes_ES_flux, LTER=="UMR(Jankowski)")[, c("yi", "vi")], 
           study_labels = filter(wrtds_slopes_ES_flux, LTER=="UMR(Jankowski)")[, "site"],
           xlab = "Sagehen: slope of DSi flux by year",
           variant = "rain")
j

ggarrange(a,b,c,d,e,f,g,h,i,j, ncol=5, nrow=2)



viz_forest(x = wrtds_slopes_ES_flux[, c("yi", "vi")], 
           xlab = "slope of DSi flux by year (Z-transformed)",
           group=wrtds_slopes_ES_flux[, "LTER"],
           study_labels = wrtds_slopes_ES_flux[, "site"],
           variant = "rain",
           summary_label = c("Summary(LTER = AND)",
                  "Summary(LTER = ARC)",
                  "Summary(LTER = KRR(Julian))",
                  "Summary(LTER = HBR)",
                  "Summary(LTER = LMP(Wymore))",
                  "Summary(LTER = LUQ)",
                  "Summary (LTER = MCM)",
                  "Summary (LTER = NWT)",
                   "Summary(LTER = Sagehen(Sullivan))",
                   "Summary(LTER = UMR(Jankowski))"))

```




```{r}

# fit <- nlme(data=wrtds, FNConc_mgL ~ Year, random = ~LTER)
# 
# fit <- lmer(data=wrtds2, FNConc_mgL ~ Year +1|LTER)
# summary(fit)

```

# Using WRTDS trend estimates

> hmm some have 95% CIs in the 90 million-ish range so let's scrap those for now

```{r}

ggplot(wrtds_trends, aes(LTER_site, estC)) +
  geom_point()+
  geom_linerange(aes(ymin = lowC95, ymax = upC95))+
  coord_flip()+
  geom_hline(yintercept = 0)+
  scale_x_discrete(limits = rev)

```


```{r}
wrtds_trends %>% 
  arrange(lowC95)

wrtds_trends %>% 
  arrange(desc(upC95))


ggplot(wrtds_trends, aes(estC))+
  geom_histogram()

ggplot(wrtds_trends, aes(lowC95))+
  geom_histogram()

ggplot(wrtds_trends, aes(upC95))+
  geom_histogram()

wrtds_trends %>% 
  filter(lowC95 < -2e7)

wrtds_trends %>% 
  filter(upC95 > 2e7)

wrtds_trends_trimmed <- wrtds_trends %>% 
  filter(lowC95>-50) %>% 
  filter(upC95<50)

```


```{r}
summary(wrtds_trends_trimmed)

ggplot(wrtds_trends_trimmed, aes(site, estC)) +
  geom_point()+
  geom_linerange(aes(ymin = lowC95, ymax = upC95))+
  coord_flip()+
  geom_hline(yintercept = 0)+
  scale_x_discrete(limits = rev)+
  facet_wrap(~LTER, scales='free')


#trying to make summary points per LTER didn't work this way

# ggplot(wrtds_trends_trimmed) +
#   geom_point(aes(site, estC))+
#   geom_linerange(aes(site, ymin = lowC95, ymax = upC95))+
#   coord_flip()+
#   geom_hline(yintercept = 0)+
#   scale_x_discrete(limits = rev)+
#   stat_summary(aes(LTER, fun = mean, geom = "point")) + 
#   stat_summary(aes(LTER, fun.data = mean_cl_normal,
#                geom = "pointrange", fun.args = list(mult = 1)))+
#   facet_wrap(~LTER, scales='free')

```

> calculating a rough estimate of standard error from the 95% CIs for now, but need to make sure this is ok to do (should still give a relatively good weighting for meta-regression stuff for now/makes sense when compared to the CIs)

```{r}
wrtds_trends_trimmed <- wrtds_trends_trimmed %>% 
  mutate(SE_est = ((upC95-lowC95)/2)/sqrt(duration))

ggplot(wrtds_trends_trimmed, aes(site, SE_est))+
  geom_point()+
  coord_flip()
```

> trying to do a meta-regression model for each LTER because that's the only way I know how to get overall weighted effect sizes for each LTER, but metafor doesn't like whatever I'm doing

```{r eval=FALSE, include=FALSE}


wrtds_trends_ES <- escalc(measure="GEN", ri=estC, vi=SE_est,
                          data=wrtds_trends_trimmed)

mod1<-rma.mv(yi=estC,
          vi=SE_est,
          data=filter(wrtds_trends_trimmed, LTER=="AND"),
          random = ~site)

summary(mod1)

filter(wrtds_trends_trimmed, LTER=="AND")



ggplot(filter(wrtds_corr, variable=='Conc_mgL'), aes(site, ri)) +
  geom_point()+
  #geom_linerange(aes(ymin = lowC95, ymax = upC95))+
  coord_flip()+
  geom_hline(yintercept = 0)+
  scale_x_discrete(limits = rev)+
  facet_wrap(~LTER, scales='free')

```

>likelihood vs pval stuff to check out how those are all related

```{r}

wrtds_trends %>% count(rejectC)

ggplot(wrtds_trends, aes(pValC, rejectC))+
  geom_point()+
  geom_vline(xintercept=.05)

ggplot(wrtds_trends, aes(likeCDown, rejectC))+
  geom_point()+
  geom_vline(xintercept=.05)

ggplot(wrtds_trends, aes(likeCUp, rejectC))+
  geom_point()+
  geom_vline(xintercept=.95)

```


# maps and latitude (non)effects

> importing lat-long data and having a quick look- looks like Sagehen needs to swap hemispheres

```{r}
latlongs <- read_csv("LongTermWatersheds_LatLong.csv") %>% 
  rename(site=Stream.Site)

leaflet(latlongs) %>%
  addTiles() %>% 
  addMarkers(lng = ~Longitude, lat = ~Latitude, popup = ~ LTER)

latlongs <- latlongs %>% 
  mutate(Longitude = ifelse(LTER=='Sagehen', -Longitude, Longitude))

leaflet(latlongs) %>%
  addTiles() %>% 
  addMarkers(lng = ~Longitude, lat = ~Latitude, popup = ~ LTER)



a <- unique(wrtds_trends$site) #usi this to check where there are differences in the colnames
b <- unique(latlongs$site)
setdiff(b,a)
b %in% a
which(a %in% b)

```


```{r}
wrtds_trends2 <- left_join(wrtds_trends, latlongs, by='site')
wrtds_slopes_ES_Si2 <- left_join(wrtds_slopes_ES_Si, latlongs, by="site")
wrtds_slopes_ES_discharge2 <- left_join(wrtds_slopes_ES_discharge, latlongs, by="site")
wrtds_slopes_ES_flux2 <- left_join(wrtds_slopes_ES_flux, latlongs, by="site")

```


> joining with slope data- here these represent untransformed values of the slopes ("real" slope units of change per time from WRTDS trend estimates I think) where all above forest plots were Z-transformed

```{r}

pal <- colorBin(palette = "RdBu", bins = c(-6,-3,-2,-1,0,1,2,3,6), domain = wrtds_trends$estC, reverse = TRUE)

#pal <- colorNumeric("RdBu", wrtds_trends$estC)

leaflet(wrtds_trends2) %>%
  addTiles() %>% 
  addCircleMarkers(lng = ~Longitude,
             lat = ~Latitude,
             #popup = ~ LTER.x,
             color="black",
             stroke=TRUE,
             fillColor = ~pal(estC),
             fillOpacity = 10,
             opacity = .5,
             label = ~paste0(wrtds_trends2$LTER.x,"::", wrtds_trends2$site, ", slope: ", estC),
             radius = 10) 

# I don't think the legend is super helpful..

  # addLegend(position = "bottomleft",
  #                 pal = pal,
  #                 values = range(wrtds_trends$estC),
  #                 title = "WRTDS slope estimate (DSi~year)")


```

## meta-regression including absolute latitude as variable

>plotting absolute lat vs slopes for DSi/discharge/flux

```{r}
ggplot(wrtds_trends2, aes(abs(Latitude), estC))+
  geom_point()+
  geom_smooth(method='lm')

ggplot(wrtds_slopes_ES_Si2, aes(abs(Latitude), estimate))+
  geom_point()+
  geom_smooth(method='lm')+
  ylab('slope DSi from annual estimates')

ggplot(wrtds_slopes_ES_discharge2, aes(abs(Latitude), estimate))+
  geom_point()+
  geom_smooth(method='lm')+
  ylab('slope discharge from annual estimates')

ggplot(wrtds_slopes_ES_flux2, aes(abs(Latitude), estimate))+
  geom_point()+
  geom_smooth(method='lm')+
  ylab('slope DSi flux from annual estimates')

```

> meta-regression stuff also shows no effect of lat, but here's where we could also plug in additional variables to see if anything modifies slopes

```{r}
mod_Si3<-rma.mv(yi,vi,
          data=wrtds_slopes_ES_Si2,
          random = ~1|site,
          mods = ~abs(Latitude))
summary(mod_Si3)


mod_discharge2<-rma.mv(yi,vi,
          data=wrtds_slopes_ES_discharge2,
          random = ~1|site,
          mods = ~abs(Latitude))
summary(mod_discharge2)

mod_flux2<-rma.mv(yi,vi,
          data=wrtds_slopes_ES_flux2,
          random = ~1|site,
          mods = ~abs(Latitude))
summary(mod_flux2)

```

